Development of Autograder For Competitive Programming Using Contestant PC As Worker

### 2019-06-29 src/paper.tex
starting 'obtaining problem test-cases'

\subsection{Program Compilation}
\subsection{Obtaining Problem Test-case}
\subsection{Handling Reverse Engineering Attack}

>>>>

\subsection{Program Compilation}

In order to evaluate contestant's submissions, we need to compile and execute the submitted source code. To compile the source code, we need a specific compiler. Every worker should has the same version of compiler. The same compiler with different version can produces different output. In order to keep the fairness of grading process, we need to distribute the same version of compiler to all workers in the system. In this work, we distribute the compiler in the autograder program to every workers. Every worker compiles the source code inside an isolated filesystem that has been installed with the same version of compilers.

\subsection{Obtaining Problem Test-cases}

Every worker needs test-cases to evaluate contestant solutions. A test-case is a pair of text file that contains input and output of the problem. Usually, the test-case files are generated by test-case generator that created by problem setters. The worker evaluates the contestant solution by executing the solution using the input test-case and compare the output with the output test-case. In order to evaluate the contestant solutions, we need to bring the problem testcases into the worker. To bring the test-cases into the worker is not easy because the test-case file can be a very large file and confidential.

\subsection{Handling Reverse Engineering Attack}
